Giant Low Surface Brightness Galaxies As Merger Remnants

### 2015-12-05 glsb.tex
fund plane decap

\begin{figure}
\epsscale{.4}
\plotone{Plots/Color_Magnitu_Diagram.eps}\plotone{Plots/Faber_Jackson_Relation.eps}\\
\plotone{Plots/Fundamental_Plane.eps}\plotone{Plots/mg_sigma.eps}
\epsscale{1}
\caption{
Top Left:  The color-magnitude diagram for 141,000 galaxies of similar redshift and magnitude as Malin 2 and UGC 6614.  Top Right:  The Faber-Jackson relation for 45,700 SDSS galaxies, along with a best-fit line.  Left:  The $r$-band Fundamental Plane from SDSS along with our GLSB galaxies and best-fit line.  Bottom Right:  The relation between central velocity dispersion and the Mg2 absorption feature.   Looking at the SDSS data, our GLSB galaxies appear as realtively typical red elliptical galaxies.  \label{elliptical_relations}}
\end{figure}

We follow \citet{Bernardi03,Bernardi03b} in fitting fundamental plane parameters to our selected SDSS galaxies.  We fit the fundamental plane by minimizing $\chi^2$ in, 
\begin{equation}
\chi^2 = \log R_0 - a \log \sigma - b \log I_0 - c
\end{equation}
where $R_0$ is the effective radius, $\sigma$ is velocity dispersion in kilometers per second and $I_0$ is the surface brightness.  The resulting best-fit parameters are  a =1.376 , b = -0.661, c = -9.938.  We note that we have not made a rigorous volume-complete selection of galaxies, rather, simply galaxies with similar magnitudes, colors, and redshifts to our GLSBs.   See \citet{Saulder13} for a more rigorous analysis of the Fundamental Plane in SDSS.

@@

The Fundamental Plane contours in Figure~\ref{elliptical_relations} was computed from:
%fund_2
\begin{verbatim}
select
ph.objid, sp.z, sp.velDisp, sp.velDisperr, deVMag_g,deVMag_r, ph.deVRad_r, 
ph.r,ph.dered_r, ph.extinction_r, ph.extinction_g, ph.deVAB_r,  gs.best_model_z, 
gse.oh_p50, gse.lgm_tot_p50, gs.model_chisq_040, gs.model_chisq_080, 
gs.model_chisq_170, gs.model_chisq_400, zoo.spiral, zoo.elliptical, 
zoo.uncertain, zoo.p_el, zoo.p_cw,zoo.p_acw

>>>>

\begin{figure}
\epsscale{.4}
\plotone{Plots/Color_Magnitu_Diagram.eps}\plotone{Plots/Faber_Jackson_Relation.eps}\\
\plotone{Plots/Fundamental_Plane.eps}\plotone{Plots/mg_sigma.eps}
\epsscale{1}
\caption{
Top Left:  The color-magnitude diagram for 141,000 galaxies of similar redshift and magnitude as Malin 2 and UGC 6614.  Top Right:  The Faber-Jackson relation for 45,700 SDSS galaxies, along with a best-fit line.  Left:  The $r$-band fundamental plane from SDSS along with our GLSB galaxies and best-fit line.  Bottom Right:  The relation between central velocity dispersion and the Mg2 absorption feature.   Looking at the SDSS data, our GLSB galaxies appear as realtively typical red elliptical galaxies.  \label{elliptical_relations}}
\end{figure}

We follow \citet{Bernardi03,Bernardi03b} in fitting fundamental plane parameters to our selected SDSS galaxies.  We fit the fundamental plane by minimizing $\chi^2$ in, 
\begin{equation}
\chi^2 = \log R_0 - a \log \sigma - b \log I_0 - c
\end{equation}
where $R_0$ is the effective radius, $\sigma$ is velocity dispersion in kilometers per second and $I_0$ is the surface brightness.  The resulting best-fit parameters are  a =1.376 , b = -0.661, c = -9.938.  We note that we have not made a rigorous volume-complete selection of galaxies, rather, simply galaxies with similar magnitudes, colors, and redshifts to our GLSBs.   See \citet{Saulder13} for a more rigorous analysis of the fundamental plane in SDSS.

@@

The fundamental plane contours in Figure~\ref{elliptical_relations} was computed from:
%fund_2
\begin{verbatim}
select
ph.objid, sp.z, sp.velDisp, sp.velDisperr, deVMag_g,deVMag_r, ph.deVRad_r, 
ph.r,ph.dered_r, ph.extinction_r, ph.extinction_g, ph.deVAB_r,  gs.best_model_z, 
gse.oh_p50, gse.lgm_tot_p50, gs.model_chisq_040, gs.model_chisq_080, 
gs.model_chisq_170, gs.model_chisq_400, zoo.spiral, zoo.elliptical, 
zoo.uncertain, zoo.p_el, zoo.p_cw,zoo.p_acw
